---
name: Mariana
surname: Montes
# position: "PhD Student, Linguistics"
address: "Erasmushuis, Faculty of Arts, KU Leuven"
profilepic: avatar.jpg
www: www.marianamontes.me
email: "mariana.montes@kuleuven.be"
github: marianamontes
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Linguist interested in Cognitive and Corpus linguistics and Data visualization"
output:
  vitae::moderncv:
    latex_engine: xelatex
skills: "R,5"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

 * I was born and raised in Argentina
 * I like languages and linguistics
 * I like empirical methods and visual analytics

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Why,
   "PhD in Linguistics", "2017-2021", "KU Leuven", "Leuven, Belgium", "Defended: 21/Sep/2021",
  "Lincenciatura in Italian Language and Literature", "2011-2016", "Universidad Nacional de Córdoba", "Córdoba, Argentina", "Cumulative GPA: 9.25/10"
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Why)
```

# Teaching experience

```{r}
tribble(
  ~Year, ~Course, ~University, ~Where, ~Program,
  "Sep-Dec 2021", "Lexical Semantics and Lexicology (Substitute)", "KU Leuven", "Leuven, Belgium", "Advanced Master in Linguistics",
  "Sep-Dec 2020", "Lexical Semantics and Lexicology (Collaborator, with Dirk Geeraerts)", "KU Leuven", "Leuven, Belgium", "Advanced Master in Linguistics",
  "Jan 2020", "Distributional Semantics (Collaborator, with Dirk Geeraerts)", "Tilburg University", "Tilburg, Netherlands", "Winter LOT School",
  "Sep-Dec 2019", "Lexicology and Morphology (Collaborator, with Dirk Geeraerts)", "KU Leuven", "Leuven, Belgium", "Master in Linguistics",
  "Sep-Dec 2018", "Lexicology and Morphology (Collaborator, with Kris Heylen)", "KU Leuven", "Leuven, Belgium", "Master in Linguistics",
  "Mar 2016-Oct 2017", "Linguistics I (TA, with Silvana Marchiaro)", "Universidad Nacional de Córdoba", "Córdoba, Argentina","Degree in Italian Language and Literature (Licenciatura, Profesorado, Traductorado)"
) %>%
  detailed_entries(
    what = Course, when = Year, with = University, where = Where, why = Program
  )
```

# Invited talks

```{r}
tribble(
  ~Year, ~Title, ~University, ~Where, ~Event,
  "6 Nov 2021", "Métodos distribucionales y visualización aplicados a la semántica lexica (Distributional methods and visualization applied to lexical semantics)", "Grupo de Estadística para el Estudio del Lenguaje, Universidad de Buenos Aires", "Online", "Ciclo de charlas sobre Herramientas y métodos para el análisis cuantitativo del lenguaje",
  "1 Oct 2021", "Nephological Semantics (with Karlien Franco)", "Universidad del Salvador", "Buenos Aires, Argentina (and via YouTube)", "II Jornadas de Lingüística y Gramática Española"
) %>%
  detailed_entries(
    what = Title, when = Year, with = University, where = Where, why = Event
  )
```

# Awards

```{r}
tribble(
  ~Year, ~What, ~With,
  2020, "DATATHON: 3rd place in Best Visualization", "KU Leuven",
  2018, "DATATHON: 3rd place in Best Visualization", "KU Leuven",
  2017, "Award for highest GPA in the cohort and timely graduation", "Universidad Nacional de Córdoba"
) %>% 
  brief_entries(what = What, when = Year, with = With)
```

# Languages

- Spanish (native)
- English (advanced)
- Italian (advanced)
- Dutch (intermediate-advanced)
- Japanese (intermediate)
- French (basic)

# Skills

- R (advanced)

- Python (intermediate)

- Javascript (intermediate, mostly D3)

# Publications

<!-- TODO Filter and translate publications -->

```{r}
library(tidyverse)

bibliography_entries("publications.bib") %>%
  mutate(leading = if_else(nchar(author$family) == 0, editor$family, author$family)) %>% 
  arrange(leading, issued)
```

